A Fast Unified Model for Parsing and Sentence Understanding

### 2016-05-29 writing/hard_stack_paper/batching_fig.tex
Edits to pp. 1-4.
Incremental paper update. Off to lunch.
Re-style acknowledgments, batching figure.

\begin{subfigure}[t]{\columnwidth}
\begin{center}
\scalebox{0.75}{
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black] 
    \tikzstyle{alt}=[fill=orange!40]
    \pgfsetarrowsend{latex}
    \tikzstyle{fwd} = [draw=black, line width=1pt]

@@

\begin{subfigure}[t]{\columnwidth}
\begin{center}
\scalebox{0.75}{
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]
    \tikzstyle{alt}=[fill=orange!40]    
    \pgfsetarrowsend{latex}
    \tikzset{edge from parent/.append style={<-, line width=1pt}}

@@

\caption{An illustration of two standard designs for sentence encoders. The TreeRNN, unlike the sequence-based RNN, requires a substantially different connection structure for each sentence, making batched computation impractical.}
\end{figure}

>>>>

\begin{subfigure}[t]{\columnwidth}
\begin{center}
\scalebox{0.8}{
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black] 
    \tikzstyle{alt}=[fill=orange!40]
    \pgfsetarrowsend{latex}
    \tikzstyle{fwd} = [draw=black, line width=1pt]

@@

\begin{subfigure}[t]{\columnwidth}
\begin{center}
\scalebox{0.8}{
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt]
    \tikzstyle{alt}=[fill=orange!40]    
    \pgfsetarrowsend{latex}
    \tikzset{edge from parent/.append style={<-, line width=1pt, >=latex}}

@@

\caption{\label{fig:batching} An illustration of two standard designs for sentence encoders. The TreeRNN, unlike the sequence-based RNN, requires a substantially different connection structure for each sentence, making batched computation impractical.}
\end{figure}

### 2016-05-29 writing/hard_stack_paper/paper.tex
Acknowledgments.
Re-style acknowledgments, batching figure.

\author{
Samuel R.\ Bowman$^{1,2,5,}$\thanks{~\,The first two authors contributed equally.} \\
\texttt{\small sbowman@stanford.edu} \\
\And
Jon Gauthier$^{2,3,5,*}$ \\
\texttt{\small jgauthie@stanford.edu} \\
\And
Abhinav Rastogi$^{4,5}$ \\
\texttt{\small arastogi@stanford.edu} \\
\AND
Raghav Gupta$^{2,5,6}$ \\
\texttt{\small rgupta93@stanford.edu} \\
\And
Christopher D.\ Manning$^{1,2,5,6}$\\
\texttt{\small manning@stanford.edu}\\
\And
Christopher Potts$^{1}$\\
\texttt{\small cgpotts@stanford.edu}
\AND\\[-3ex]
{$^{1}$Stanford Linguistics\quad
$^{2}$Stanford NLP Group\quad
$^{3}$Stanford Symbolic Systems}\\
{$^{4}$Stanford Electrical Engineering\quad
$^{5}$Stanford AI Lab\quad
$^{6}$Stanford Computer Science}
}

@@

We acknowledge financial support from a Google Faculty Research Award, the Stanford Data Science Initiative, and the National Science Foundation under grant no.~BCS 1456077. Some of the Tesla K40s used for this research were donated by the NVIDIA Corporation.

>>>>

\author{
Samuel R.\ Bowman$^{1,2,3,}$\thanks{~\,The first two authors contributed equally.} \\
\texttt{\small sbowman@stanford.edu} \\
\And
Jon Gauthier$^{2,3,4,*}$ \\
\texttt{\small jgauthie@stanford.edu} \\
\And
Abhinav Rastogi$^{3,5}$ \\
\texttt{\small arastogi@stanford.edu} \\
\AND
Raghav Gupta$^{2,3,6}$ \\
\texttt{\small rgupta93@stanford.edu} \\
\And
Christopher D.\ Manning$^{1,2,3,6}$\\
\texttt{\small manning@stanford.edu}\\
\And
Christopher Potts$^{1}$\\
\texttt{\small cgpotts@stanford.edu}
\AND\\[-3ex]
{$^{1}$Stanford Linguistics\quad
$^{2}$Stanford NLP Group\quad
$^{3}$Stanford AI Lab}\\
{$^{4}$Stanford Symbolic Systems\quad
$^{5}$Stanford Electrical Engineering\quad
$^{6}$Stanford Computer Science}
}

@@

We acknowledge financial support from a Google Faculty Research Award, the Stanford Data Science Initiative, and the National Science Foundation under grant no.~BCS 1456077. Some of the Tesla K40s used for this research were donated by the NVIDIA Corporation. We also thank Kelvin Gu, Noah Goodman, and many others in the Stanford NLP group for helpful comments.
